Wu-Tang Clan

### 2015-03-03 rmtw/a5/latex8.tex
Spellcheck
Changed tense

\subsubsection{Review Protocol}
Subsequently, the reivew protocol was defined. The list of databases included can be seen in Table I. The included databases have been chosen based on recommendations in \cite{brereton2007lessons}. SpringerLink was included as advised in \cite{kitchenham2007guidelines}. The databases were divided evenly between the two researchers.

@@

The digital libraries, mentioned in section Table 1 were chosen for their extensive catalogues, reliability and availability of the data. Hand searching of journals was not performed as we decided to limit the scope of the search to digital libraries, conferences and other sources.

Given that MDSD is a relatively new process, we have decided to limit the search starting in 1990 to the current date. We feel that this limitation on the search will not hinder our results as we were unable to find any papers published prior to this date concerning MDSD.

The selection criteria for the papers will be further refined during this stage. After applying the initial exclusion and inclusion criteria, we can exclude and include based on practicality. Below is a short list of these criteria.

@@

The Quality of the papers must also be considered before they are examined for use in the study. Determination of paper quality will be performed after initial exclusions and inclusions have been performed. These additional quality checks will seek to eliminate papers with excessive bias, quality of the paper and the reliability of the results.

@@

To assess the reliability of the inclusions and exclusions, Fleiss' kappa index will be applied on both researchers findings. All conflicts regarding to acceptance of papers will be discussed and resolved prior to their inclusion in the SLR. Ideally, the kappa rating achieved will be from 0.61 - 0.80 indicating a strong alignment between the researchers.

Furthermore, as per the suggestion from Kitchenham \cite{kitchenham2007guidelines} after the application of the inclusion and exclusion criteria any paper failing to meet these criteria will be retained and shown in the results of the SLR.

@@

In order to accurately and objectively collect all data, the use of data collection forms is highly recommended \cite{kitchenham2007guidelines}. These forms will be created and the pilot tested by the researchers taking part in the study. This allows the researchers to discover potential issues before the study takes place, such as ambiguity of questions in the form.

The data extraction will be performed by both researchers on each individual study, meaning each study is extracted twice. By doing this, the chance for bias and misinterpretation is reduced. As suggested by Kitchenham \cite{kitchenham2007guidelines}, care must be taken to avoid the acceptance of duplicate studies of the same data. In the case of duplication, the most robust study will be chosen.

@@

\Section{Acknowledgements}

>>>>

\subsubsection{Review Protocol}
Subsequently, the review protocol was defined. The list of databases included can be seen in Table I. The included databases have been chosen based on recommendations in \cite{brereton2007lessons}. SpringerLink was included as advised in \cite{kitchenham2007guidelines}. The databases were divided evenly between the two researchers.

@@

The digital libraries, mentioned in section Table 1, were chosen for their extensive catalogues, reliability and availability of the data. Hand searching of journals was not performed as we decided to limit the scope of the search to digital libraries, conferences and other sources.

Given that MDSD is a relatively new process, we decided to limit the search starting to papers published 1990 to the current date. We feel that this limitation on the search did not hinder the results as we were unable to find any papers published prior to this date concerning MDSD.

The selection criteria for the papers was further refined during this stage. After applying the initial exclusion and inclusion criteria, exclusions and inclusions were based on practicality. Below is a short list of these criteria.

@@

The Quality of the papers was also considered before they were examined for use in the study. Determination of paper quality occurred after initial exclusions and inclusions had been performed. These additional quality checks sought to eliminate papers with excessive bias, low quality and the unreliable results.

@@

To assess the reliability of the inclusions and exclusions, Fleiss' kappa index was applied on both researchers findings. All conflicts regarding to acceptance of papers was discussed and resolved prior to their inclusion in the SLR. The initial kappa rating achieved was 0.78, which lies in the band 0.61 - 0.80 indicating a strong alignment between the researchers.

Furthermore, as per the suggestion from Kitchenham \cite{kitchenham2007guidelines} after the application of the inclusion and exclusion criteria any paper failing to meet these criteria was retained and will be shown in the results of the SLR.

@@

In order to accurately and objectively collect all data, the use of data collection forms is highly recommended \cite{kitchenham2007guidelines}. We created and pilot tested these forms prior to the data extraction. This allowed us to discover potential issues before the study took place, such as ambiguity of questions in the form.

The data extraction was performed by both researchers on each individual study, meaning each study was extracted twice. By doing this, the chance for bias and misinterpretation was reduced. As suggested by Kitchenham \cite{kitchenham2007guidelines}, care was taken to avoid the acceptance of duplicate studies of the same data. In the case of duplication, the most robust study was chosen.

@@

\Section{Acknowledgements}
John had the main responsibility for sections 1.2, 1.3, 2.0. William had the main responsibility for sections 1.0, 1.1, 2.1, 2.2. The research questions were written together. We have, however, worked on all sections jointly - and all sections have been reviewed by both William and John.
